The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}

### 2021-07-08 Draft.tex
Bin durch

\section{Introduction}
When trying to transfer an already existing method on a relatively new platform, 
it's important to know the things that come with being on such a platform and the 
possible influences those things might have on the method.\\\\

In day-to-day usage of online platforms and services it's not uncommon to face some 
issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
particularly different to those. Therefore, we want to discuss, in this paper, to 
which extent these problems can influence the test-results of being on such an 
'issue-infected' platform in contrast to a well running platform with no issues.\\\\

We tried to focus on the most frequent issues we faced in our experience of browsing 
on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
\newpage
\section{Materials and Methodes}
\subsection{Summary}
To which extend do commen networks problems in an eLearning-Environment
influence the academic performance of students. This information can be used to
re-evaluate the eLearning-Environment.

@@

\subsection{}

\begin{figure}
    \includegraphics[width=\textwidth]{UML Prototyp.PNG}
    \caption{A logic flow chart , representing how an implementation could operate.
    The black circle is the user interacting with the software. The webside would
    consist of two parts. A frontend handling user interaction and the creation of {\itshape bugs}.
    The backend responsible for saving the collected data and ensuring the frontend
    remains operationale.} \label{fig1}
\end{figure}

\clearpage
\section{Results}
The results are displayed in chronological order of the analysis, there is
no emphisis on the significans given by the order itself.

\subsection{Control Group(50f/50m) vs Error Group(50f/50m)}
\begin{figure}[!h]
    \begin{minipage}{0.43\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the control group (50f/50m) and
        the error group (50f/50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig2}
    \end{minipage}
\hfill
\begin{minipage}{0.43\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the control group (50f/50m) the error group (50f/50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & control group & error group \\
        \hline
        median & 53.0&43.5 \\
        \hline
        standart deviation & 29.278&29.826 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.728} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.467} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Control Group(50f) vs Error Group(50f)}
\begin{figure}[!h]
    \begin{minipage}{0.43\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the control group (50f) and
        the error group (50f).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig3}
    \end{minipage}
\hfill
\begin{minipage}{0.43\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the control group (50f) the error group (50f).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & control group & error group \\
        \hline
        median & 55.5&40.0 \\
        \hline
        standart deviation & 27.85&30.933 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.949} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.345} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Control Group(50m) vs Error Group(50m) }
\begin{figure}
    \begin{minipage}{0.43\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the control group (50m) and
        the error group (50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig4}
    \end{minipage}
\hfill
\begin{minipage}{0.43\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the control group (50m) the error group (50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & control group & error group \\
        \hline
        median & 52.5&50.5 \\
        \hline
        standart deviation & 30.638&28.495 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.08} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.936} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

@@

The study can make a general statement on network problems. However not all possible
problems are simulated. It is possible that a problem exists that does affect the academic performance of
students significantly. Also longterm effects can not be discoverd by this study since it is very time limited.
Futhermore designflaws of the eLearning-Environment or limited to no access to a computer are problems that
are overlooked or ignored. These problems require additional studys.
\section{Conclusion}
In this paper we could clearly see the impact of platform-issues on the students performance in an 
exam-scenario and it is not significant. There might still be certain aspect of long-term-effects,
which we couldn't simulate due to our test setup, because there was a slight worsening happening 
when comparing our outcomes. It would be very interesting to see, how much significance such things 
like errors will show  in a long run with more variables included.
\section{Refernces}
\begin{thebibliography}{8}
    \bibitem{ref_soft}
    Github, \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}. Last accessed 8 Jul 2021
    \end{thebibliography}
\end{document}

>>>>

\section{Introduction}
When trying to transfer an already existing method on a relatively new platform, 
it's important to know the things that come with being on such a platform and the 
possible influences those things might have on the method.\\

In day-to-day usage of online platforms and services it's not uncommon to face some 
issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
particularly different to those. Therefore, we want to discuss, in this paper, to 
which extent these problems can influence the test-results of being on such an 
'issue-infected' platform in contrast to a well running platform with no issues.\\

We focused on commen network issues.Which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.
\section{Materials and Methodes}
\subsection{Summary}
To which extend do commen networks problems in an eLearning-Environment
influence the academic performance of students. This information can be used to
re-evaluate the eLearning-Environment.

@@

\subsection{Procedure}
The participants are welcomed and thanked for their time.
The students were randomly selected for either the controll group or the test group
prospective known as the error group. Then the students where placed infront of a computer
which was either manipulated or untouched based on their group.They then create an account
and start solving the questions.
After they finished all questions they log out.
The students are rewarded with cookies and again thanked for their time.

\begin{figure}
    \includegraphics[width=\textwidth]{UML Prototyp.PNG}
    \caption{A logic flow chart , representing how an implementation could operate.
    The black circle is the user interacting with the software. The webside would
    consist of two parts. A frontend handling user interaction and the creation of {\itshape bugs}.
    The backend responsible for saving the collected data and ensuring the frontend
    remains operationale.} \label{fig1}
\end{figure}
\newpage
\section{Results}
The results are displayed in chronological order of the analysis, there is
no emphisis on the significans given by the order itself. The following data is
what we would expect in an actual experiment. To recreate the data see \cite{ref_soft}.

\subsection{Control Group(50f/50m) vs Error Group(50f/50m)}
\begin{figure}[!h]
    \begin{minipage}{0.4\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the control group (50f/50m) and
        the error group (50f/50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig2}
    \end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the control group (50f/50m) the error group (50f/50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & control group & error group \\
        \hline
        median & 53.0&43.5 \\
        \hline
        standart deviation & 29.278&29.826 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.728} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.467} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Control Group(50f) vs Error Group(50f)}
\begin{figure}[!ht]
    \begin{minipage}{0.4\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the control group (50f) and
        the error group (50f).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig3}
    \end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the control group (50f) the error group (50f).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & control group & error group \\
        \hline
        median & 55.5&40.0 \\
        \hline
        standart deviation & 27.85&30.933 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.949} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.345} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Control Group(50m) vs Error Group(50m) }
\begin{figure}[!h]
    \begin{minipage}{0.43\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the control group (50m) and
        the error group (50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig4}
    \end{minipage}
\hfill
\begin{minipage}{0.43\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the control group (50m) the error group (50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & control group & error group \\
        \hline
        median & 52.5&50.5 \\
        \hline
        standart deviation & 30.638&28.495 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.08} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.936} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

@@

The study can make a general statement on network problems. However not all possible
problems are simulated. It is possible that a problem exists that does affect the academic performance of
students significantly. Also longterm effects can not be discoverd by this study since it is very time limited.
Futhermore designflaws of the eLearning-Environment are also overlooked or ignored.
These problems require additional studys.
\section{Conclusion}
In this paper we could clearly see the impact of platform-issues on the students performance in an 
exam-scenario and it is not significant. There might still be certain aspect of long-term-effects,
which we couldn't simulate due to our test setup, because there was a slight worsening happening 
when comparing our outcomes. Futher studys should focus on the longterm effect of technical problems
to deepen our understanding of the technology.
\section{Refernces}
\begin{thebibliography}{8}
    \bibitem{ref_soft}
    Github, \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}. Last accessed 8 Jul 2021
    \end{thebibliography}
\end{document}
